Architectures and Open pNets

### 2018-11-21 2018-Arch-pNets/arch-pNets.tex
work on substitution lemmas
Eric: figure 4 = Timer open automaton

	\noindent
\begin{mathpar}
    \mprset {vskip=1ex}
\inferrule
    {
\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{g} 
\\
\\     	
	\forall m\!\!\in\!\! I_1. {\pNet_m 
	\models\openrule
    	{
    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\openrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {\alpha_m}
    		\ostate{s_m'}} }\\\\
     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
    }
    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\openrule
    		{
    		{\beta_j}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
\end{mathpar}

@@

\Fig{enc:nopri} shows the encoding of the Failure Monitor
architecture, including the encodings of the two coordinators, \ie
$\nopri[\NameTimer]$ and $\nopri[\NameCtrl]$.  Notice that the
encoding in the figure is slightly optimised: some of the ports do not
have an associated Boolean value, nor the additional loop transitions.
\todoSB{Revise this if necessary}\hl{We will explicitate this optimisation once we have defined the
encoding of the interaction model.}

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{FailureTimerPNET-v4}
  \caption{The pNET encoding the Failure Monitor architecture (without the priority model)}
  \label{fig:FailureTimer:pNet}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{FailureTimerZonePNET}
  \caption{The pNET encoding the Failure Monitor architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}

@@

\begin{semantics}
The semantics of $\ac(P)$ is given by the function $|\cdot| : \ac(P)
\rightarrow \ai(P)$ (we use the $\sum$ and $\prod$ notation for,
respectively, the union and fusion of multiple terms of $\ac(P)$):
%
\begin{align}
  \label{eq:acap}
  |[p]| & = p\,,
  & |x_1 + x_2| & = |x_1| + |x_2|\,,
  & \left|\prod_{i=1}^n [x_i]\,\right| & = \prod_{i=1}^n |x_k|\,,
  \\
  \label{eq:acaptrig}
  && \hspace{-2cm}\left|\prod_{i=1}^n [x_i]' \prod_{j=1}^m [y_j]\,\right| = 
  \sum_{i=1}^n |x_i| & \lefteqn{\left(
  \prod_{k\not=i}\Big(1 + |x_k|\Big)\ \prod_{j=1}^m \Big(1 + |y_j|\Big)\right)}\,
\end{align}
%
for $n > 0$, $m \geq 0$, $x_1,\dots,x_n,y_1,\dots,y_m \in \ac(P)$ and
$p\in P\cup \{0,1\}$.
\end{semantics}

>>>>

%	\noindent
%\begin{mathpar}
%    \mprset {vskip=1ex}
%\inferrule
%    {
%\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
%    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
%k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{g} 
%\\
%\\     	
%	\forall m\!\!\in\!\! I_1. {\pNet_m 
%	\models\openrule
%    	{
%    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
%    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
%  \qquad
%\forall m\!\!\in\!\! I_2.		{ \pNet_m 
%    	 \models
%    	\openrule
%    	{\emptyset, \Pred_m, \Post_m}
%    	{\ostate{s_m} \OTarrow {\alpha_m}
%    		\ostate{s_m'}} }\\\\
%     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
%    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
%    	\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
%    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
%    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
%    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
%    }
%    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
%    	\models
%    	{\openrule
%    		{
%    		{\beta_j}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
%    		\Post_m}
%    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
%    			\ostate{(s_i^\prime)^{i\in L}}}
%    	}
%    }
%\end{mathpar}  
	\noindent
\begin{mathpar}
    \mprset {vskip=.8ex}
\inferrule
    {
\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
\\
\\     	
	\forall m\!\!\in\!\! I_1. {\pNet_m 
	\models\openrule
    	{
    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \qquad
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\openrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {\alpha_m}
    		\ostate{s_m'}} }\\\\
     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
    }
    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\openrule
    		{
    		{\beta_j}^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
\end{mathpar}

@@

\Fig{fig:FailureTimer:pNet} shows the encoding of the Failure Monitor
architecture, including the encodings of the two coordinators, \ie
$\nopri[\NameTimer]$ and $\nopri[\NameCtrl]$.  Notice that the
encoding in the figure is slightly optimised: some of the ports do not
have an associated Boolean value, nor the additional loop transitions.
\todoSB{Revise this if necessary}\hl{We will explicitate this optimisation once we have defined the
encoding of the interaction model.}

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{FailureTimerPNET-v4}
  \caption{The open pNET encoding the Failure Monitor architecture (\fig{schema:ArchFailure:BIP}) without the priority model}
  \label{fig:FailureTimer:pNet}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{TimerOpenAut}
  \caption{The open Automaton of the Failure Monitor Architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}

12 open transitions... Comments on the predicates ???

Should list some temporal logic properties....

@@

\begin{semantics}
The semantics of $\ac(P)$ is given by the function $|\cdot| : \ac(P)
\rightarrow \ai(P)$ (we use the $\sum$ and $\prod$ notation for,
respectively, the union and fusion of multiple terms of $\ac(P)$):
%
\begin{align}
  \label{eq:acap}
  |[p]| & = p\,,
  & |x_1 + x_2| & = |x_1| + |x_2|\,,x
  & \left|\prod_{i=1}^n [x_i]\,\right| & = \prod_{i=1}^n |x_k|\,,
  \\
  \label{eq:acaptrig}
  && \hspace{-2cm}\left|\prod_{i=1}^n [x_i]' \prod_{j=1}^m [y_j]\,\right| = 
  \sum_{i=1}^n |x_i| & \lefteqn{\left(
  \prod_{k\not=i}\Big(1 + |x_k|\Big)\ \prod_{j=1}^m \Big(1 + |y_j|\Big)\right)}\,
\end{align}
%
for $n > 0$, $m \geq 0$, $x_1,\dots,x_n,y_1,\dots,y_m \in \ac(P)$ and
$p\in P\cup \{0,1\}$.
\end{semantics}
